\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-15 response2.tex
answered comments
Added missing "the"
Small rephrasing

\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=20mm]{geometry}
\usepackage{amsmath,color,amsthm,enumerate,amsfonts,mathtools}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{paralist}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{todonotes}

@@

\begin{response}
  We have replaced ``appropriate vertex'' with ``the root of tree in $T$ that contains $v$.''
\end{response}

@@

\begin{response}
  We have added the edge-maximal qualifier and (earlier) defined what it means for a framed graph to be edge-maximal (with respect to its frame).
\end{response}

>>>>

\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=25mm]{geometry}
\usepackage{amsmath,color,amsthm,enumerate,amsfonts,mathtools}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{paralist}
\usepackage{stmaryrd}
\usepackage{amssymb}
\usepackage{todonotes}

@@

\begin{response}
  We have replaced ``appropriate vertex'' with ``the root of the tree in $T$ that contains $v$.''
\end{response}

@@

\begin{response}
  We have added the edge-maximal qualifier and (earlier) defined what it means for a framed graph to be edge-maximal (with respect to a particular frame).
\end{response}
